Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone

### 2019-01-07 DingHickKritzMakRICAMChap.tex
Finished first draft of Section 2.

  \author[1]{Yuhan Ding}
  \author*[2]{Fred J. Hickernell}
  \author[3]{Peter Krtizer} 
  \author[4]{Simon Mak}
  \runningauthor{Y. Ding, F. J. Hickernell, P. Kritzer, and S. Mak}
  \affil[1]{...}
  \affil[2]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
  \affil[3]{...}
  \affil[4]{...}
  \title{Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone}
  \runningtitle{Adaptive Approximation}
  \subtitle{...}
  \abstract{...}
  %\keywords{...}
  %\classification[PACS]{...}
  %\communicated{...}
  %\dedication{...}
  %\received{...}
  %\accepted{...}
  %\journalname{...}
  %\journalyear{...}
  %\journalvolume{..}
  %\journalissue{..}
  \startpage{1}
  \aop
  %\DOI{...}

@@

\begin{lemma}
Let $\calK$ be some proper or improper subset of $\bbK$. Moreover, let $\rho'$ be defined the relation
\begin{equation*}
    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
\end{equation*}
\FredNote{I am trying to capture the case $\rho = \tau = 2, \ \rho' = \infty$ in \cite{DinHic20a} and the case $\rho = \infty, \ \rho' = \tau = 1$ in the work with Simon.}
Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
\begin{equation}
\label{DHKM:SOL_ineq}
    \norm[\calG]{\SOL(f)} \le \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
    \end{equation}
    \begin{multline}
    \label{DHKM:SOL_tight_ineq}
    \bigabs{\hf(\bsk)} = \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} \quad \forall \bsk \in \calK\\
    \implies \norm[\calG]{\SOL(f)} = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \ \& \ \norm[\calF]{f} = R.
    \end{multline}
Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} tight.
\end{lemma}
\begin{proof}
The proof proceeds by applying H\"older's inequality
\begin{align}
    \label{DHKM:SOL_A}
    \norm[\calG]{\SOL(f)}  
    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \hf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \hf(\bsk)  \bigr)_{\bsk \in \calK}} \\
\nonumber
    & = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\hf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
    \nonumber
    & \le \biggnorm[\rho]{\biggl(  \frac{\hf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau \\
    \nonumber
    & = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
\end{align}
which establishes inequality \eqref{DHKM:SOL_ineq}.
Substituting the formula for $\bigabs{\hf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
\begin{equation*}
       \norm[\calG]{\SOL(f)}  
    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
    = \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}.
\end{equation*}
Moreover,
\begin{equation*}
    \norm[\calF]{f}  
    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
    = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
    = \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R.
\end{equation*}
This completes the proof.
\end{proof}

Based on this lemma and taking $\calK = \bbK$, the norm of the solution operator can be expressed in terms of the $\lambda_\bsk$ as follows:
\begin{equation}
    \norm[\calF \to \calG]{\SOL}  = \sup_{\norm[\calF]{f} \le 1} \norm[\calG]{\SOL(f)} = \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \mathbb{K}}}.
\end{equation}

@@

\begin{theorem} \label{DHKM:APP_optimality_thm} Let $\calB_{R} : = \{ f \in \calF : \norm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.  The error of the approximation defined in \label{DHKM:APP_def} is bounded tightly above as 
\begin{equation} \label{DHKM:APP_errorBd}
    \sup_{f \in \calB_R} \norm[\calG]{\SOL(f) - \APP(f,n)}  \le R \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}.
\end{equation}
Moreover, the worst case error over $\calB_R$ of any approximation based on $n$ series coefficients of the input function, $\APP'(\cdot,n)$, can be no smaller.
\end{theorem}

To facilitate the proof of this theorem and theorems below, we first establish the following lemma:

\begin{lemma}
Let $\calK$ be some subset of $\bbK$.
\end{lemma}

\begin{proof}[Proof of Theorem \ref{DHKM:APP_optimality_thm}]
The proof of \eqref{DHKM:APP_errorBd} follows from an argument similar to that used to derive 
\eqref{DHKM:SOLNorm}.  The optimality of $\APP$ follows by bounding the error of an arbitrary approximation, $\APP'$ applied to functions that mimic the zero function.

 Let $\APP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.  Choose $f$ to satisfy the following conditions:
\begin{gather*}
    \hf(\bsk'_1) = \cdots = \hf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ \Bignorm[\tau]{\bigl(\hf_{\bsk}\bigr)_{\bsk \notin \calJ}}
    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
    \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}
\end{gather*}
Then $\APP'(\pm f,n) = \APP'(0,n)$, and
\begin{align*}
\MoveEqLeft{\max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(\pm f,n)}} \\
&=  \max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(0,n)} \\
& \ge \frac 12 \left [ \norm[\calG]{\SOL(f) - \APP'(0,n)} 
+ \norm[\calG]{- \SOL(f) - \APP'(0,n)}\right] \\
& \ge \norm[\calG]{\SOL(f)} 
= \Bignorm[\tau]{\bigl(\hf_{\bsk}\bigr)_{\bsk \notin \calJ}}
    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
    \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \\
    & = R  \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.
\end{align*}
The ordering of the $\lambda_{\bsk}$ implies that $\norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}$ for arbitrary $\calJ$ can be no smaller than the case $\calJ = \{\bsk_1, \ldots, \bsk_n\}$.  This completes the proof.
\end{proof}

@@

\section{Bounding the Norm of the Input Function Based on a Pilot Sample} 
\FredNote{I think that this is a simpler case than \cite{DinHic20a} or the work with Simon, so we should start with this}

@@

\begin{algorithm}
	\caption{$\ALG$ Based on a Pilot Sample\label{DHKM:PilotConeAlg}} 
	\begin{algorithmic}
	\PARAM an initial sample size, $n_1$; an inflation factor, $\frakC$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
		\INPUT a black-box function, $f$; an absolute error tolerance,
		$\varepsilon>0$

@@

\begin{theorem}
Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}.  The computational cost of this algorithm is 
\begin{equation} \label{DHKM:PilotConeAlg_cost}
    \COST(\ALG,\calC,\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le \varepsilon/(\frakC R) \right \}.
\end{equation}
and the computational complexity has the lower bound
\begin{equation}
    a
\end{equation}
\end{theorem}

\begin{proof}
The upper bound on the computational cost of this algorithm is obtained by noting that 
\begin{align*}
    \MoveEqLeft{\COST(\ALG,\calC,\varepsilon,R)} \\
    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
     & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
     \frakC \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
     \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
    \le \varepsilon \right \} \\   
     & \le \min \left \{n \ge n_1 : 
     \frakC R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
    \le \varepsilon \right \},  
\end{align*}
since $\norm[\rho]{\left( \hf(\bsk_i)/\lambda_{\bsk_i} \right)_{i=1}^{n_1}} \le R$ for all $f \in \calB_R$.  Moreover, this inequality is tight for some $f \in \calC \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.  This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.

To prove the lower complexity 
\end{proof}

Since error bound

\subsection{A subsection}

\section{The \cite{DinHic20a} case with tractability, which needs a better title}

\section{The work with Simon case, which needs a better title}

>>>>

  \author[1]{Yuhan Ding}
  \author*[2]{Fred J. Hickernell}
  \author[3]{Peter Kritzer} 
  \author[4]{Simon Mak}
  \runningauthor{Y. Ding, F. J. Hickernell, P. Kritzer, and S. Mak}
  \affil[1]{...}
  \affil[2]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
  \affil[3]{...}
  \affil[4]{...}
  \title{Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone}
  \runningtitle{Adaptive Approximation}
  \subtitle{...}
  \abstract{...}
  %\keywords{...}
  %\classification[PACS]{...}
  %\communicated{...}
  %\dedication{...}
  %\received{...}
  %\accepted{...}
  %\journalname{...}
  %\journalyear{...}
  %\journalvolume{..}
  %\journalissue{..}
  \startpage{1}
  \aop
  %\DOI{...}

@@

\begin{lemma} \label{DHKM:Key_Lem}
Let $\calK$ be some proper or improper subset of $\bbK$. Moreover, let $\rho'$ be defined by the relation
\begin{equation*}
    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
\end{equation*}
\FredNote{I am trying to capture the case $\rho = \tau = 2, \ \rho' = \infty$ in \cite{DinHic20a} and the case $\rho = \infty, \ \rho' = \tau = 1$ in the work with Simon.}
Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
\begin{equation}
\label{DHKM:SOL_ineq}
    \norm[\calG]{\SOL(f)} \le \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
    \end{equation}
    \begin{multline}
    \label{DHKM:SOL_tight_ineq}
    \bigabs{\hf(\bsk)} = \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} \quad \forall \bsk \in \calK\\
    \implies \norm[\calG]{\SOL(f)} = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \ \& \ \norm[\calF]{f} = R.
    \end{multline}
Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} tight.
\end{lemma}
\begin{proof}
The proof proceeds by applying H\"older's inequality
\begin{align}
    \label{DHKM:SOL_A}
    \norm[\calG]{\SOL(f)}  
    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \hf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \hf(\bsk)  \bigr)_{\bsk \in \calK}} \\
\nonumber
    & = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\hf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
    \nonumber
    & \le \biggnorm[\rho]{\biggl(  \frac{\hf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau \\
    \nonumber
    & = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
\end{align}
which establishes inequality \eqref{DHKM:SOL_ineq}.
Substituting the formula for $\bigabs{\hf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
\begin{equation*}
       \norm[\calG]{\SOL(f)}  
    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
    = \frac{R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}.
\end{equation*}
Moreover,
\begin{equation*}
    \norm[\calF]{f}  
    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
    = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
    = \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R.
\end{equation*}
This completes the proof.
\end{proof}

Based on this lemma and taking $\calK = \bbK$, the norm of the solution operator can be expressed in terms of the $\lambda_\bsk$ as follows:
\begin{equation} \label{DHKM:SOLNorm}
    \norm[\calF \to \calG]{\SOL}  = \sup_{\norm[\calF]{f} \le 1} \norm[\calG]{\SOL(f)} = \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \mathbb{K}}}.
\end{equation}

@@

\begin{theorem} \label{DHKM:APP_optimality_thm} Let $\calB_{R} : = \{ f \in \calF : \norm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.  The error of the approximation defined in \eqref{DHKM:APP_def} is bounded tightly above as 
\begin{equation} \label{DHKM:APP_errorBd}
    \sup_{f \in \calB_R} \norm[\calG]{\SOL(f) - \APP(f,n)}  \le R \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}.
\end{equation}
Moreover, the worst case error over $\calB_R$ of any approximation based on $n$ series coefficients of the input function, $\APP'(\cdot,n)$, can be no smaller.
\end{theorem}

\begin{proof}
The proof of \eqref{DHKM:APP_errorBd} follows from an argument similar to that used to derive 
\eqref{DHKM:SOLNorm}.  The optimality of $\APP$ follows by bounding the error of an arbitrary approximation, $\APP'$ applied to functions that mimic the zero function.

 Let $\APP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.  Use Lemma \ref{DHKM:Key_Lem} to choose $f$ to satisfy the following conditions:
\begin{gather*}
    \hf(\bsk'_1) = \cdots = \hf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ \Bignorm[\tau]{\bigl(\hf(\bsk)\bigr)_{\bsk \notin \calJ}}
    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
    \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}
\end{gather*}
Then $\APP'(\pm f,n) = \APP'(0,n)$, and
\begin{align*}
\MoveEqLeft{\max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(\pm f,n)} =  \max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(0,n)}} \\
& \ge \frac 12 \left [ \norm[\calG]{\SOL(f) - \APP'(0,n)} 
+ \norm[\calG]{- \SOL(f) - \APP'(0,n)}\right] \\
& \ge \norm[\calG]{\SOL(f)} 
= \Bignorm[\tau]{\bigl(\hf(\bsk)\bigr)_{\bsk \notin \calJ}}
    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
    \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \\
    & = R  \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.
\end{align*}
The ordering of the $\lambda_{\bsk}$ implies that $\norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}$ for arbitrary $\calJ$ can be no smaller than the case $\calJ = \{\bsk_1, \ldots, \bsk_n\}$.  This completes the proof.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Bounding the Norm of the Input Function Based on a Pilot Sample} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\FredNote{I think that this is a simpler case than \cite{DinHic20a} or the work with Simon, so we should start with this}

@@

\begin{algorithm}
	\caption{$\ALG$ Based on a Pilot Sample\label{DHKM:PilotConeAlg}} 
	\begin{algorithmic}
	\PARAM an initial sample size, $n_1 \in \N$; an inflation factor, $\frakC > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
		\INPUT a black-box function, $f$; an absolute error tolerance,
		$\varepsilon>0$

@@

\begin{theorem}
Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}.  The computational cost of this algorithm is 
\begin{equation} \label{DHKM:PilotConeAlg_cost}
    \COST(\ALG,\calC,\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le \varepsilon/(\frakC R) \right \}.
\end{equation}
The computational complexity has the lower bound
\begin{equation} \label{DHKM:PilotConeAlg_comp}
        \COMP(\calA(\calC),\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le 2\varepsilon/[(1 - 1/\frakC) R] \right \}.
\end{equation}
\end{theorem}

\begin{proof} \FredNote{Fred is working on this proof.}
The upper bound on the computational cost of this algorithm is obtained by noting that 
\begin{align*}
    \MoveEqLeft{\COST(\ALG,\calC,\varepsilon,R)} \\
    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
     & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
     \frakC \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
     \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
    \le \varepsilon \right \} \\   
     & \le \min \left \{n \ge n_1 : 
     \frakC R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
    \le \varepsilon \right \},  
\end{align*}
since $\norm[\rho]{\left( \hf(\bsk_i)/\lambda_{\bsk_i} \right)_{i=1}^{n_1}} \le \norm[\calF]{f} \le R$ for all $f \in \calB_R$.  Moreover, this inequality is tight for some $f \in \calC \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.  This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.

To prove the lower complexity bound, let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC$ in \eqref{DHKM:pilot_cone}.   Fix $R$ and $\varepsilon$ arbitarily.  Define $\calK_1 := \{\bsk_1, \ldots, \bsk_{n_1}\}$.  Two fooling functions will be constructed of the form $f_\pm = f_1 \pm f_2$.

The input function $f_1$ is defined via its series coefficients as in Lemma \ref{DHKM:Key_Lem}, having nonzero coefficients only for $\bsk \in \calK_1$:
\begin{equation*}
    \bigabs{\hf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/\frakC) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
    0, & \bsk \notin \calK_1,
    \end{cases}
   \qquad \norm[\calF]{f_1} = \frac{R(1 + 1/\frakC)}{2}.
\end{equation*}
Suppose that $\ALG'(f_1,\varepsilon)$ samples the series coefficients $f_1(\bsk)$ for $\bsk \in \calJ$, and let $n$ denote the cardinality of $\calJ$.

Now, construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$ and also as in Lemma \ref{DHKM:Key_Lem}:
\begin{gather}
\nonumber
    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/\frakC) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
    0, & \bsk \in \calJ, 
    \end{cases}
    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/\frakC)}{2}, \\
    \label{DHKM:SOLf2bd}
    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
\end{gather}
Let $f_{\pm} = f_1 \pm f_2$.  By the definitions above, it follows that
\begin{align}
    \norm[\calF]{f_{\pm}} &= \norm[\calF]{ f_1 \pm f_2 } \le \norm[\calF]{ f_1} + \norm[\calF]{ f_2 } =  R, \\
    \nonumber
    \norm[\rho]{\left( \frac{\hf_\pm(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} 
    & = \norm[\rho]{\left( \frac{\hf_1(\bsk_i) \pm \hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
    \nonumber
    & \ge \norm[\rho]{\left( \frac{\hf_1(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} - \norm[\rho]{\left( \frac{\hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
    \nonumber
    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{\frakC} \\
    & \ge \frac{\norm[\calF]{f_{\pm}}}{\frakC}.
\end{align}
Therefore, $f_\pm \in \calC \cap \calB_R$.  Moreover, since the series coefficients for $f_\pm$ are the same for $\bsk \in \calJ$, it follows that $\ALG'(f_+,\varepsilon) = \ALG'(f_-,\varepsilon)$.  Thus, $\SOL(f_{\pm})$ must be similar to each other.

Using an argument like that in the proof of  Theorem \ref{DHKM:APP_optimality_thm}, it follows that 
\begin{align*}
\varepsilon & \ge \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{\pm},\varepsilon)} 
=  \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{+},\varepsilon)} \\
& \ge \frac 12 \left [ \norm[\calG]{\SOL(f_{+}) - \ALG'(f_{+},\varepsilon)} 
+ \norm[\calG]{\SOL(f_{-}) - \ALG'(f_{+},\varepsilon)}  \right] \\
& \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
=\frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
& \ge \frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
\end{align*}
by the ordering of the $\bsk_i$.  This inequality implies complexity bound \eqref{DHKM:PilotConeAlg_comp}.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tracking the Decay Rate of the Fourier Coefficients} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\FredNote{The \cite{DinHic20a} case with tractability}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{
.0
.
.} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\FredNote{The work with Simon}
